Disease Knowledge Transfer across Neurodegenerative Diseases

### 2019-03-26 paper/paper.tex
finished validation on ADNI subtypes

\begin{table}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}{c | c c c c c c}
\textbf{Model} & \textbf{Cingulate} & \textbf{Frontal} & \textbf{Hippo.} & \textbf{Occip.} & \textbf{Parietal} & \textbf{Temporal}\\
& \multicolumn{6}{c}{\textbf{Prediction Error (MSE)}}\\
DKT & 0.09$\pm$0.04 & 0.03$\pm$0.01 & 0.18$\pm$0.03 & 0.04$\pm$0.02 & 0.06$\pm$0.02 & 0.04$\pm$0.02\\
Latent stage & 0.09$\pm$0.04 & 0.03$\pm$0.01 & 0.17$\pm$0.03 & 0.04$\pm$0.02 & 0.06$\pm$0.02 & 0.04$\pm$0.02\\
Linear & 0.05$\pm$0.02* & 0.15$\pm$0.04* & 0.09$\pm$0.03* & 0.07$\pm$0.03* & 0.07$\pm$0.02* & 0.07$\pm$0.02*\\
& \multicolumn{6}{c}{\textbf{Rank Correlation (Spearman rho)}}\\
DKT  & 0.76  & 0.48  & 0.76  & 0.55  & 0.55  & 0.33 \\
Latent stage & 0.76  & 0.49  & 0.80*  & 0.56  & 0.51*  & 0.33 \\
Linear & 0.48*  & 0.31*  & 0.64*  & 0.61*  & 0.57*  & 0.27* \\
\end{tabular}
% \normalfont
\caption[Performance evaluation of DKT and two simpler models]{Performance evaluation of DKT and two simpler models. (*) Statistically significant difference in the performance of DKT vs latent-stage/linear models, based on a two-tailed t-test, Bonferroni corrected.}
% \end{footnotesize}
\label{sec:dktPerfMetrics}
\end{table}

>>>>

\begin{table}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}{c | c c c c c c}
\textbf{Model} & \textbf{Cingulate} & \textbf{Frontal} & \textbf{Hippo.} & \textbf{Occip.} & \textbf{Parietal} & \textbf{Temporal}\\
& \multicolumn{6}{c}{\textbf{ADNI Subtypes: Hippocampal to Cortical}}\\
DKT &      0.56 $\pm$ 0.23 &    0.35 $\pm$ 0.17 &        0.58 $\pm$ 0.14 &     -0.10 $\pm$ 0.29 &     0.71 $\pm$ 0.11 &     0.34 $\pm$ 0.26 \\
Latent stage &      0.44 $\pm$ 0.25 &    0.34 $\pm$ 0.21 &       0.34 $\pm$ 0.24* &     -0.07 $\pm$ 0.22 &     0.64 $\pm$ 0.16 &    0.08 $\pm$ 0.24* \\
Multivariate &      0.60 $\pm$ 0.18 &   0.11 $\pm$ 0.22* &       0.12 $\pm$ 0.29* &     -0.22 $\pm$ 0.22 &   -0.44 $\pm$ 0.14* &   -0.32 $\pm$ 0.29* \\
Spline &    -0.24 $\pm$ 0.25* &  -0.06 $\pm$ 0.27* &        0.58 $\pm$ 0.17 &     -0.16 $\pm$ 0.27 &    0.23 $\pm$ 0.25* &    0.10 $\pm$ 0.25* \\
Linear &    -0.24 $\pm$ 0.25* &   0.20 $\pm$ 0.25* &        0.58 $\pm$ 0.17 &     -0.16 $\pm$ 0.27 &    0.23 $\pm$ 0.25* &    0.13 $\pm$ 0.23* \\
& \multicolumn{6}{c}{\textbf{tAD to Posterior Cortical Atrophy}}\\
DKT  & 0.76  & 0.48  & 0.76  & 0.55  & 0.55  & 0.33 \\
Latent stage & 0.76  & 0.49  & 0.80*  & 0.56  & 0.51*  & 0.33 \\
Linear & 0.48*  & 0.31*  & 0.64*  & 0.61*  & 0.57*  & 0.27* \\
\end{tabular}
% \normalfont
\caption[Performance evaluation of DKT and two simpler models]{Performance evaluation of DKT and two simpler models. (*) Statistically significant difference in the performance of DKT vs latent-stage/linear models, based on a two-tailed t-test, Bonferroni corrected.}
% \end{footnotesize}
\label{sec:dktPerfMetrics}
\end{table}
